---
title: "MSFA_GroupG_Part2"
author: "Veronique"
date: "26/09/2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

The raw dataset is the IMDB information about the movies shown between 1916 and 2016 (August), scrapted by Kaggle user chuansun76 from IMDB website. It contains 28 variables and 5043 observations. In order to reduce the influences  inflation and exchange rate fluctuation have on the money-related variables (e.g. gross revenue), and to make the social media-related variable more consistent, we narrow down the data time frame to between 2011 and 2016. Moreover, in case of different measure of currency for movie gross earnings, we only focus on US movies which uses U.S. dollar as currency measure in this report. After deleting the variables that have N/A values and that veriables that are less relevant to the aim of our report, our final variables are:

```{r results = "asis", echo = FALSE}
library(knitr)
#library(stargazer)
#library(xtable)
#options(xtable.floating = FALSE)
#options(xtable.timestamp = "")

Variable_name <- c("movie_title", "title_year", "director_name", "duration", "gross", "genres", "num_voted_users", "num_user_for_reviews", "num_critic_for_reviews",	"budget", "imdb_score", "movie_facebook_likes", "actor_1_name", "actor_2_name", "actor_3_name")
Explanation <- c("Movie's title.", "The year the movie released.", "Main director's name.", "Length of the movie.", "Gross box office earnings of the movie in US dollar.", "Genres of the movie. The movie could be multi-genres; the report will explain in detail how we deal with this problem before the analysis.", "Number of IMDB users who voted for the movie rating.", "Number of IMDB users who wrote reviews for the movie.", "Number of critics who wrote reviews for the movie.", "Total budget for the movie in US dollar. Some numbers are estimated; they are based on media reports and are often supplied by sources close to the production.", "IMDB average score (out of 10).", "Total likes of the movie's facebook page (up to Aug 2016).", "Main actor/actress 1.", "Main actor/actress 2.", "Main actor/actress 3.")
variable_table <- data.frame(Variable_name, Explanation)

kable(variable_table, caption = "Variables")

#print(xtable::xtable(variable_table, caption = "Variables", type = "html", html.table.attributes = "border=0"))

#stargazer::stargazer(variable_table, type = "html", title = "Variables")

```

There are certain limitations that worth being pointed out.

Firstly, due to the mismatched timing, the variable movie_facebook_likes is not as accurate as other variables. Social media is indeed an important aspect to reflect the popularity of a movie, but it is an accumulating number. Our data was collected in August 2016, no matter when the movie was shown. Therefore the number of facebook likes could be less fair for recent movies, e.g. movies shown in 2016. To reduce the influence, it would be more accurate to use the movie data between 2011 and 2015 in the descriptive analysis, and then use the 2016 movies in the predictive analysis.  

Secondly, the social popularity index for the cast in the the original dataset cannot reflect how good the actor perform. Therefore we will use a stronger index instead of the original ones: the award winning index. It is the sum of the Oscar award won by the three main actor/actress and the director.

Thirdly, the numbers of voters, user reviews and critic reviews on IMDB are absolute values.


